---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# bbcharts

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/bbcharts)](https://cran.r-project.org/package=bbcharts)
<!-- badges: end -->

The goal of bbcharts is to provide an interface to the Billboards top charts. 

## Installation

You can install the latest version of bbcharts from GitHub with:

``` r
remotes::install_github("josiahparry/bbcharts")
```

## Example

The "Hot 100" Billboard Chart 

```{r}
library(bbcharts)

bb_chart("hot-100")
```

Use `bbcharts` in conjunction with [`genius`](https://github.com/josiahparry/genius) to get the lyrics for songs on the top charts.

```{r alt}
library(dplyr)
library(genius)
alt <- bb_chart("alternative-songs")

alt_lyrics <- alt %>% 
  # get only the first 5 songs
  slice(1:5) %>% 
  # add lyrics to a data frame
  add_genius(artist, title, type = "lyrics")

alt_lyrics

```

## List possible charts

You can view all possible charts to query from using the `chart_table` that is exported.

```{r}
bbcharts::chart_table
```


